### 2023-06-07 docs/paper/paper.tex
Initial paper intro and thoughts

%%
%% This is file `sample-sigconf.tex',
%% generated with the docstrip utility.
%%
%% The original source files were:
%%
%% samples.dtx  (with options: `sigconf')
%% 
%% IMPORTANT NOTICE:
%% 
%% For the copyright see the source file.
%% 
%% Any modified versions of this file must be renamed
%% with new filenames distinct from sample-sigconf.tex.
%% 
%% For distribution of the original source see the terms
%% for copying and modification in the file samples.dtx.
%% 
%% This generated file may be distributed as long as the
%% original source files, as listed above, are part of the
%% same distribution. (The sources need not necessarily be
%% in the same archive or directory.)
%%
%%
%% Commands for TeXCount
%TC:macro \cite [option:text,text]
%TC:macro \citep [option:text,text]
%TC:macro \citet [option:text,text]
%TC:envir table 0 1
%TC:envir table* 0 1
%TC:envir tabular [ignore] word
%TC:envir displaymath 0 word
%TC:envir math 0 word
%TC:envir comment 0 0
%%
%%
%% The first command in your LaTeX source must be the \documentclass command.
\documentclass[sigconf]{acmart}

%%
%% \BibTeX command to typeset BibTeX logo in the docs
\AtBeginDocument{%
  \providecommand\BibTeX{{%
    Bib\TeX}}}

%% Rights management information.  This information is sent to you
%% when you complete the rights form.  These commands have SAMPLE
%% values in them; it is your responsibility as an author to replace
%% the commands and values with those provided to you when you
%% complete the rights form.
\setcopyright{acmcopyright}
\copyrightyear{2023}
\acmYear{2023}
\acmDOI{XXXXXXX.XXXXXXX}

%% These commands are for a PROCEEDINGS abstract or paper.
\acmConference[ICCDA '23]{}{July, 2023}{GuiYang, CN}
\acmPrice{15.00}
\acmISBN{978-1-4503-XXXX-X/23/07}

%%
%% Submission ID.
%% Use this when submitting an article to a sponsored event. You'll
%% receive a unique submission ID from the organizers
%% of the event, and this ID should be used as the parameter to this command.
%%\acmSubmissionID{123-A56-BU3}

%%
%% For managing citations, it is recommended to use bibliography
%% files in BibTeX format.
%%
%% You can then either use BibTeX with the ACM-Reference-Format style,
%% or BibLaTeX with the acmnumeric or acmauthoryear sytles, that include
%% support for advanced citation of software artefact from the
%% biblatex-software package, also separately available on CTAN.
%%
%% Look at the sample-*-biblatex.tex files for templates showcasing
%% the biblatex styles.
%%

%%
%% The majority of ACM publications use numbered citations and
%% references.  The command \citestyle{authoryear} switches to the
%% "author year" style.
%%
%% If you are preparing content for an event
%% sponsored by ACM SIGGRAPH, you must use the "author year" style of
%% citations and references.
%% Uncommenting
%% the next command will enable that style.
%%\citestyle{acmauthoryear}

%%
%% end of the preamble, start of the body of the document source.
\begin{document}

%%
%% The "title" command has an optional parameter,
%% allowing the author to define a "short title" to be used in page headers.
\title{Decoupled Data Science - Tools for flexible, reproducible eScience}

%%
%% The "author" command and its associated commands are used to define
%% the authors and their affiliations.
%% Of note is the shared affiliation of the first two authors, and the
%% "authornote" and "authornotemark" commands
%% used to denote shared contribution to the research.
\author{John Hawkins}
\email{john.hawkins@Getting-Data-Science-Done.com}
\orcid{1234-5678-9012}
\affiliation{%
  \institution{Getting-Data-Science-Done.com}
  \city{Sydney}
  \state{NSW}
  \country{Australia}
  \postcode{2000}
}

\renewcommand{\shortauthors}{Hawkins}

\begin{abstract}
\end{abstract}

%% The code below is generated by the tool at http://dl.acm.org/ccs.cfm.
%% Please copy and paste the code instead of the example below.

\begin{CCSXML}
<ccs2012>
<concept>
<concept_id>10002951.10003260.10003261</concept_id>
<concept_desc>Information systems~Web searching and information discovery</concept_desc>
<concept_significance>500</concept_significance>
</concept>
<concept>
<concept_id>10002951.10003260.10003277.10003280</concept_id>
<concept_desc>Information systems~Web log analysis</concept_desc>
<concept_significance>500</concept_significance>
</concept>
<concept>
<concept_id>10010147.10010257</concept_id>
<concept_desc>Computing methodologies~Machine learning</concept_desc>
<concept_significance>500</concept_significance>
</concept>
</ccs2012>
\end{CCSXML}

\ccsdesc[500]{Information systems~Web searching and information discovery}
\ccsdesc[500]{Information systems~Web log analysis}
\ccsdesc[500]{Computing methodologies~Machine learning}

\keywords{Data Science, Experiment Tracking, Reproducible Science, Metadata Tracking}

\maketitle

\section{Introduction}

Progress in scientific research depends heavily on accurate record keeping of previous
experimental approaches and results. Failure to maintain these records impedes progress
by making it difficult to reproduce work, or imposing the costs of repeatedly testing 
failed lines of experimentation. This cost becomes particularly high in the age of the
reproducibility crisis, as a many teams running the same experiments in parallel, without
knowledge of each others work, has produced a factory line of un-reproducible results.

Many Machine Learning experimentation frameworks focus on the task of making experiments
easier to execute and deploy into production systems\cite{Alberti:2018,MolnerDomenech:2020}. 
To do so they are often constructed for specific combinations of technology. This is a necessary limitation 
to enable efficiency, but has the effect of limiting general applicability.
Many other eScience frameworks focus on the lineage and management of data, referred to as 
the so-called provenance problem \cite{Sahoo:2008,Conquest:2021}
The goal of the provenance frameworks is sufficient auditibiliy of data sources that will 
render eScience transparent and repeatable.

Other frameworks and approaches focus on understanding how to do large scale collaborative science, or
facilitate meta-level learning of various kinds\cite{Hunter:2005,Liu:2023}. The better we track the
process of science as a whole, the better we can understand both how to improve scientific processes
as well as data mine the history of science for phenomena that were difficult to detect.

\section{Methodology}

We begin by discussing all desirable elements required of an open science framework. These are drawn
from observations of both how collabroative science works and the successful components of distributed
scientific endeavours. These requirements are drawn from both sciences that are typically dependent
on computational frameworks (computer science, bioinformatics, physics) and those that generally are not
(social science, psychology).

The key elements are as follows:

\begin{itemize}
 \item Provenance of Data Sources
 \item Record of Data Processing
 \item Reuse of Datasets
 \item Tracking of Experiments and Results
 \item Comparison of Methods and Results
 \item Generation of Documentation
 \item Reproducibility of Projects
 \item Facilitation of Meta-Analysis
\end{itemize}

\subsection{Data}

\subsection{Features}

\subsection{Feature Importance}

\section{Results}

\section{Conclusion}

\section{Acknowledgments}

\bibliographystyle{ACM-Reference-Format}
\bibliography{refs}

\end{document}
\endinput

### 2023-06-07 docs/paper/BUILD.sh

@@ -1,0 +1,9 @@
+#!/bin/bash
+
+bibtex paper
+
+bibtex paper
+ 
+pdflatex paper.tex
+
+

### 2023-06-19 docs/paper/paper.tex
Paper updates

@@
 %% allowing the author to define a "short title" to be used in page headers.
-\title{Decoupled Data Science - Tools for flexible, reproducible eScience}
+\title{Projit: An Open Source tool for Decoupled Data Science}
 
@@
 \begin{abstract} 
+Scientific practice has expanded to become increasingly dependent of digitial technologies,
+large scale data processing and advanced analytical methods. These shifts have demanded new
+methods of implementing and recording the details of scientific projects. Monolothic applications
+have the advantage of a single and consistent design, however they impede the ability of users to
+innovate and incrementally improve processes. We discuss the qualities of an ideal eScience framework
+for building multi-stage collaboration scinetific workflows and present an open source implementation
+for managing scientific processes in a decoupled fashion that permits both flexible implementation of
+any stage of processing, and greater ease of meta-data analysis.
 \end{abstract}
-
-%% The code below is generated by the tool at http://dl.acm.org/ccs.cfm.
-%% Please copy and paste the code instead of the example below.
-
-\begin{CCSXML}
-<ccs2012>
-<concept>
-<concept_id>10002951.10003260.10003261</concept_id>
-<concept_desc>Information systems~Web searching and information discovery</concept_desc>
-<concept_significance>500</concept_significance>
-</concept>
-<concept>
-<concept_id>10002951.10003260.10003277.10003280</concept_id>
-<concept_desc>Information systems~Web log analysis</concept_desc>
-<concept_significance>500</concept_significance>
-</concept>
-<concept>
-<concept_id>10010147.10010257</concept_id>
-<concept_desc>Computing methodologies~Machine learning</concept_desc>
-<concept_significance>500</concept_significance>
-</concept>
-</ccs2012>
-\end{CCSXML}
-
-\ccsdesc[500]{Information systems~Web searching and information discovery}
-\ccsdesc[500]{Information systems~Web log analysis}
-\ccsdesc[500]{Computing methodologies~Machine learning}
 
@@
 We begin by discussing all desirable elements required of an open science framework. These are drawn
-from observations of both how collabroative science works and the successful components of distributed
+from observations of both how collaborative science works and the successful components of distributed
 scientific endeavours. These requirements are drawn from both sciences that are typically dependent
@@
 \begin{itemize}
- \item Provenance of Data Sources
- \item Record of Data Processing
- \item Reuse of Datasets
- \item Tracking of Experiments and Results
- \item Comparison of Methods and Results
- \item Generation of Documentation
- \item Reproducibility of Projects
- \item Facilitation of Meta-Analysis
+ \item Sources: Provenance of Data Sources
+ \item Processing: Record of Data Processing
+ \item Reuse: Facilitating Reuse of Datasets
+ \item Tracking: Tracking of Experiments and outputs
+ \item Results: Comparison of Methods and Results
+ \item Documentation: Generation of Documentation
+ \item Reproduction: Reproducibility of Projects
+ \item Meta-Analysis: Facilitation of Meta-Analysis
 \end{itemize}
 
-\subsection{Data}
+The elements in this list are organised in an approximately sequential manner. However, as we discuss
+them below it should be apparent that there are many ways in which these elements support each other.
+Firstly, and foremost, aata driven projects
+require a method of accessing the required \textbf{source} data and will need to maintain records 
+of this data provenance. There will typically be \textbf{processing} applied to these datasets to 
+render them applicable to experimentation and analysis. An ideal tool will track the sequential 
+nature of this processing as well as store information about the location of each resulting dataset.
+The data processed in this way is then available for \textbf{reuse} across experiments and analysis,
+making \textbf{results} comparable and facilitating \textbf{meta-analysis}.
 
-\subsection{Features}
+\subsection{Projit Process}
 
-\subsection{Feature Importance}
+The central design principle of \textit{projit} is that the decoupling of data science 
+should be achieved through utilisation of a simple metadata store. Each aspect of 
+data science work can be allowed to proceed without awareness of the structure of 
+any other element as long as it can access the information it requires through this
+metadata store.
+
+\begin{figure*}
+\includegraphics[scale=0.6]{./Projit_decoupled_process.drawio.png}
+\caption{Projit Process for Decoupled Data Science}
+\label{fig:projit}
+\end{figure*}
+
+In Figure \ref{fig:projit} we see that the core steps of data preparation, experimentation
+and analysis of results all happen independently. Each of them accesses the projit store for
+the information they need, storing information
+
+\subsection{Application}
 

### 2023-06-21 docs/paper/paper.tex
More references and literature review

@@
 the so-called provenance problem \cite{Sahoo:2008,Conquest:2021}
-The goal of the provenance frameworks is sufficient auditibiliy of data sources that will 
-render eScience transparent and repeatable.
+The goal of the provenance frameworks is sufficient auditibiliy of data that will 
+render eScience transparent and repeatable. This can be auditing of data from multiple source systems,
+or it can be auditing of logs generated during data processing\cite{Ferdous2020}. Regardless of the
+specific data to be audited, these frameworks focus on developing unified systems and processes so
+that auditing can be easily performed over many projects.
 
-Other frameworks and approaches focus on understanding how to do large scale collaborative science, or
+In addition to systems for storage of data, eScience application may include facilities for orchestration
+of data processes and services\cite{Subramanian2013}, analysis of results, generation of insights
+and documentation.
+
+Frameworks for eScience will typically need to take a position on the extent to which they are domain
+specific, versus general purpose. A domain specific approach that integrates multiple data sources in
+a domain aware fashion can faciliate automated or assisted scientific discover\cite{Howe2008}. On the
+other hand a general purpose framework facilitates multi-disciplinary collaboration and permits meta-analysis
+that transcends the boundaries of disciplines.
+
+Other frameworks and approaches in eScience focus on understanding how to do large scale collaborative science, or
 facilitate meta-level learning of various kinds\cite{Hunter:2005,Liu:2023}. The better we track the
@@
  \item Documentation: Generation of Documentation
- \item Reproduction: Reproducibility of Projects
+ \item Reproducibility: Facilitate reproduction of results
  \item Meta-Analysis: Facilitation of Meta-Analysis
@@
 them below it should be apparent that there are many ways in which these elements support each other.
-Firstly, and foremost, aata driven projects
-require a method of accessing the required \textbf{source} data and will need to maintain records 
-of this data provenance. There will typically be \textbf{processing} applied to these datasets to 
+
+First and foremost, data driven projects require a access to the required \textbf{source} data 
+and need to maintain records of this data provenance for \textbf{reproducibility}. 
+There will typically be \textbf{processing} applied to these datasets to 
 render them applicable to experimentation and analysis. An ideal tool will track the sequential 
-nature of this processing as well as store information about the location of each resulting dataset.
+nature of this \textbf{processing} as well as store information about the location of each resulting dataset.
 The data processed in this way is then available for \textbf{reuse} across experiments and analysis,
-making \textbf{results} comparable and facilitating \textbf{meta-analysis}.
+making \textbf{results} comparable.
+
+The centralised storage of data in a unified format allows for scripted generation of \textbf{documentation},
+and facilitates easy \textbf{meta-analysis}. If the product metadata is stored in a public or open source
+repository then it is possible to build tools that extract and process the data from multiple projects. It
+will permit the emgergence of an ecosystem of tools that mine the history of experiments conducted on the
+same or similar source data, evaluate experimental protocols or algorithms across projects and potentially
+automate some forms of \textbf{meta-analysis}.
+
+To achieve these advantages we require a uniform system for storing all necessary data that are inputs and outputs 
+for each stage of a data science experiment. The central store permits decoupling of processes by allowing each
+element of the process to be implemented and executed independently of the others.
 
@@
 
-\subsection{Application}
+\subsection{Implementation}
 
-\section{Results}
+Projit has been implemented as python package that functions as both a command line application
+and library that can be included inside other scripts and applications. The command line application
+can be used to query the project metadata in much the same way that the git application can be used.
+A user can add, modify and list the collection of data assets in the project: datasets, experiments 
+and results are all accessible from the command line application.
+
+The python package can be included in a script so that the script can access the project metadata store.
+This allows the script to find the location of common datasets, register themselves as an experiment
+and store results once the script is complete. Programmatic interaction with the project data through
+the projit API is what permits the scripts of a project to be decoupled and contribute to the project
+without being aware of how any other element is structured or implemented.
+
+\section{Case Study}
+
+We have utilised the projit application across multiple data science projects to store reusable datasets
+and the results of all experiments. Additionally, the metadata store contains infomation about the number
+of times each experiment has been executed, and the execution time utilised on each run. This allows us
+to generate an ad hoc script that can compare projects in terms of the data used, the number of experiments
+conducted and the total execution time. This script is constructed for illustrative purposes to show that
+the projit tool can permit arbitrary meta-analysis of projects through the standardised metadata stored across
+git repositories.
 

### 2023-06-26 docs/paper/paper.tex
Paper update

@@
 render eScience transparent and repeatable. This can be auditing of data from multiple source systems,
-or it can be auditing of logs generated during data processing\cite{Ferdous2020}. Regardless of the
+auditing of logs generated during data processing\cite{Ferdous2020}. At the extreme we can seek to
+quantify every transformation that happens to data in the course of processing\cite{Sahoo2009}. 
+Regardless of the
 specific data to be audited, these frameworks focus on developing unified systems and processes so
@@
 In addition to systems for storage of data, eScience application may include facilities for orchestration
-of data processes and services\cite{Subramanian2013}, analysis of results, generation of insights
-and documentation.
+of data processes and external services\cite{Subramanian2013}, requests for experiments with specific 
+parameters\cite{Hunter:2005}, or integrated analysis of results, generation of insights and documentation. 
+Other frameworks and approaches in eScience focus on understanding how to do large scale collaborative science, or
+facilitate meta-level learning of various kinds\cite{Hunter:2005,Liu:2023}. The better we track the
+process of science as a whole, the better we can understand both how to improve scientific processes
+as well as data mine the history of experimental results for phenomena that were difficult to detect.
 
@@
 other hand a general purpose framework facilitates multi-disciplinary collaboration and permits meta-analysis
-that transcends the boundaries of disciplines.
+that transcends the boundaries of disciplines. The other key dimension for a decision is the extent to
+which an eScience application depends on specific technologies, many machine learning science platforms
+can provide efficiency gains, but only when using specfic libraries and frameworks\cite{Alberti:2018,MolnerDomenech:2020}.
+Similarly, other empirical science platforms are built on specific database, webserver or application
+frameworks, which make them less extensible and harder to integrate.
 
-Other frameworks and approaches in eScience focus on understanding how to do large scale collaborative science, or
-facilitate meta-level learning of various kinds\cite{Hunter:2005,Liu:2023}. The better we track the
-process of science as a whole, the better we can understand both how to improve scientific processes
-as well as data mine the history of science for phenomena that were difficult to detect.
+In this work we argue for development of data science frameworks that are minimal in expectations, both in
+terms of appplication domains and underlying technologies. We present a design framework for building
+decoupled data science tools that can improve efficiency and replication through standardisation, without
+unreasonable impositions on design decisions. We describe the design of a open source project integration
+tool (\textit{projit}) that can be used either as a CLI or python API. Internally \textit{projit} depends 
+only on a metadata store that uses the general purpose JSON format. 
+As such it is trivial for developers to build interfaces in other
+languages, or devise web service APIs for decentralised versions. We explore a case study of comparing results
+across multiple projects for which we have used the \textit{projit} application to manage our metadata.
 
 \section{Methodology}
+
+\begin{figure*}
+\includegraphics[scale=0.6]{./Projit_decoupled_process.drawio.png}
+\caption{Projit Process for Decoupled Data Science}
+\label{fig:projit}
+\end{figure*}
 
@@
 
-\begin{figure*}
-\includegraphics[scale=0.6]{./Projit_decoupled_process.drawio.png}
-\caption{Projit Process for Decoupled Data Science}
-\label{fig:projit}
-\end{figure*}
+In Figure \ref{fig:projit} we see that the core steps of data preparation, experimentation
+and analysis of results all happen independently. Each of them accesses the projit metadata 
+store for the information they need, and subsequently store information and results once complete.
+This process means that in principle the location of an underlying dataset could change without
+modifying other elements of the project. Similarly, we might change the parameters or an experiment
+or the set of metrics we calculate. Each experiment and analysis task operates independently of the
+others, and all that suffers when changes are made is the potential for comparison across equal
+dimensions of variation.
 
-In Figure \ref{fig:projit} we see that the core steps of data preparation, experimentation
-and analysis of results all happen independently. Each of them accesses the projit store for
-the information they need, storing information
+In addition to the dominant requirements of experimentation (parameter and results) we store the results
+of each experimental execution as well as the experiment duration, measured from the time of initiation
+to completion. These records are particularly important in data science and machine learning where we
+may want to trade off performance with computational requirements. But these values could be used to store
+information about real world experimtal execution, or the time required to marshal and sequence a series
+of independent web services.
 

### 2023-06-28 projit/__init__.py
Working on tag implementation - modifying CLI to add tags, list assets with tags

@@ -1,4 +1,4 @@
-__version__ = "0.1.11"
+__version__ = "0.1.12"
 
 from .utils import locate_projit_config
 from .projit import projit_load

### 2023-06-28 projit/cli.py

@@ -65,6 +65,7 @@ def task_status(project):
     print("  Description: %s" % project.desc)
     print("  Datasets: %i" % len(project.datasets))
     print("  Experiments: %i" % len(project.experiments))
+    print("  Executions: %i" % len(project.executions))
     print("")
 
 ##########################################################################################
@@ -73,7 +74,7 @@ def filler(current, max_len, content=" "):
 
 ##########################################################################################
 def print_header(header):
-    full_header = header + ("_" * (80-len(header)))
+    full_header = header + ("_" * (90-len(header)))
     print(full_header)
 
 ##########################################################################################
@@ -111,38 +112,112 @@ def task_compare(project, datasets, metric, markdown):
         print(results)
 
 
+def extract_max_tags_lengths(project, asset, tags):
+    if asset in project.tags:
+        tagset = project.tags[asset]
+        max_tag_lengths = []
+        for t in tags:
+            temp = []
+            for a in tagset:
+                if t in tagset[a]:
+                    temp.append(len(tagset[a][t]))
+                else:
+                    temp.append(0)
+            max_val = max(temp)
+            if max_val<len(t):
+               max_val = len(t)
+            max_tag_lengths.append(max_val)
+        return max_tag_lengths
+    else:
+        return [0 for x in tags]
+
+
 ##########################################################################################
-def task_list(subcmd, project, dataset, markdown):
+def task_list(subcmd, project, dataset, markdown, tags):
     """
     List content of a project from the command line
     """
+    if len(tags) > 0:
+        tags_max_len = max([len(x) for x in tags])
+    else:
+        tags = []
+        tags_max_len = 0
+
     print()
     if subcmd == "datasets":
         print_header("__Datasets")
         if len(project.datasets.keys()) > 0:
+            tag_header = ""
+            if len(tags)>0:
+               tag_max_lengths = extract_max_tags_lengths(project, "dataset", tags)
+               for tag,tag_len in zip(tags,tag_max_lengths):
+                   tag_header = tag_header + tag + filler(len(tag), tag_len+3, "_")
+                
             long_key = max([len(k) for k in project.datasets.keys()])
-            myhead = "__Name" + filler(len("Name"), long_key+3, "_") + "Path_"
+            myhead = "__Name" + filler(len("Name"), long_key+3, "_") + tag_header + "Path_________"
[…]

### 2023-06-28 projit/config.py

@@ -5,4 +5,5 @@ properties_file = "properties.yaml"
 data_file = "data.json"
 experiments_file = "experiments.json"
 execution_file = "executions.json"
+tag_file = "tags.json"
 lock_file = "LOCK"

### 2023-06-28 projit/projit.py

@@ -11,6 +11,7 @@ import os
 from .config import lock_file
 from .config import config_file
 from .config import execution_file
+from .config import tag_file
 from .config import config_folder
 from .template import load_template
 from .utils import locate_projit_config
@@ -37,7 +38,9 @@ class Projit:
                  params={},
                  hyperparams={},
                  dataresults={},
-                 executions={}):
+                 executions={},
+                 tags={}
+    ):
         """
         Initialise a projit project object.
         This class will be used for storing and retrieving all data about the project,
@@ -90,6 +93,9 @@ class Projit:
                                            }
                                        }
         :type executions: Dictionary of Dictionary of Dictionary, optional
+ 
+        :param tags: The dictionary of tags for project assets.
+        :type tags: Dictionary of Dictionary of Dictionary, optional
 
         :return: None 
         :rtype: None 
@@ -104,7 +110,7 @@ class Projit:
         self.hyperparams = hyperparams
         self.dataresults = dataresults
         self.executions = executions
-
+        self.tags = tags
 
     def get_root_path(self):
         """
@@ -267,6 +273,21 @@ class Projit:
         self.save()
         self.release_lock()
 
+    def dataset_exists(self, name):
+        """
+        Check if a given dataset is in the data structure
+
+        :param name: The dataset name
+        :type name: string, required
+
+        :return: exists
+        :rtype: Boolean
+        """
+        for elem in self.datasets:
+            if elem == name:
+                return True
+        return False
+
     def experiment_exists(self, name):
         """
         Check if a given experiment is in the data structure
@@ -281,6 +302,48 @@ class Projit:
             if elem[0] == name:
                 return True
         return False
+ 
+    def validate_asset(self, asset, name):
+        if asset=="experiment":
+            return self.experiment_exists(name)
+        elif asset=="dataset":
+            return self.dataset_exists(name)
+        else:
+            return False
+
+    def add_tags(self, asset, name, vals):
+        self.initiate_lock()
+        self.reload()
+        assets = {}
+        assets[name] = {}
+        if asset in self.tags:
+            assets = self.tags[asset]
+            if name not in assets:
+                assets[name] = {}
+        for val in vals:
+            split = val.split("=")
+            assets[name][split[0]] = split[1]
+
+        self.tags[asset] = assets
+        self.save()
+        self.release_lock()
+
[…]

### 2023-07-25 docs/paper/paper.tex
Fixing bug in CLI - updating references

@@
 innovate and incrementally improve processes. We discuss the qualities of an ideal eScience framework
-for building multi-stage collaboration scinetific workflows and present an open source implementation
-for managing scientific processes in a decoupled fashion that permits both flexible implementation of
+for building multi-stage collaboration scientific workflows and present an open source implementation
+for managing data science processes in a decoupled fashion that permits both flexible implementation of
 any stage of processing, and greater ease of meta-data analysis.
@@
 failed lines of experimentation. This cost becomes particularly high in the age of the
-reproducibility crisis, as a many teams running the same experiments in parallel, without
-knowledge of each others work, has produced a factory line of un-reproducible results.
+reproducibility crisis where many teams are running the same experiments in parallel, without
+knowledge of each others work, and producing a factory line of un-reproducible results 
+\cite{Ioannidis2005}.
 
@@
 can be used to query the project metadata in much the same way that the git application can be used.
-A user can add, modify and list the collection of data assets in the project: datasets, experiments 
-and results are all accessible from the command line application.
+A user can add, modify and list the collection of analytical assets in the project: datasets, experiments 
+parameters, tags and results are all accessible from the command line application.
 
@@
 the projit API is what permits the scripts of a project to be decoupled and contribute to the project
-without being aware of how any other element is structured or implemented.
+without being aware of how any other element is structured or implemented. Furthermore, as the metadata
+is stored locally in standard JSON files, these can be stored inside a cloud repository and then contributed
+to by collaborators. This allows distributed data science teams to define their own lines of experimentation,
+but use a synchronised data set then continually contribute to a central meta-data store of project results.
 

### 2023-07-25 projit/cli.py

@@ -417,10 +417,11 @@ def print_usage(prog):
     print("   ", prog, "plot initial execution                  # Plot the execution times for the experiment named 'initial'")
     print("   ", prog, "plot initial hyperparam alpha           # Plot the change in hyperparam 'alpha' for the experiment named 'initial'")
     print("   ", prog, "plot initial result MSE                 # Plot the change in result 'MSE' for the experiment named 'initial'")
-    print("   ", prog, "-m list results test                    # List results on 'test' data in markdown")
+    print("   ", prog, "render path_to_output.pdf               # Render a PDF document summarising the project")
+    print("   ", prog, "-m list results test                    # List results on 'test' data in Markdown format")
     print("   ", prog, "rm experiment explore                   # Remove the experiment explore (requires confirmation)")
     print("   ", prog, "rm experiment .                         # Remove all experiments (requires confirmation)")
-    print("   ", prog, "-m list results test                    # List results on test data in markdown")
+    print("   ", prog, "-m list results test                    # List results on test data in Markdown format")
     print("   ", prog, "compare dataone,datatwo MAE             # Compare results over datasets using metric MAE")
     print("")
 
@@ -442,6 +443,7 @@ def cli_main():
    parser = argparse.ArgumentParser()
    parser.add_argument('-v', '--version', help='Print Version', action='store_true')
    parser.add_argument('-m', '--markdown', help='Use markdown for output', action='store_true')
+   parser.add_argument('-u', '--usage', help='Print detailed usage instructions with examples', action='store_true')
 
    subparsers = parser.add_subparsers(dest="cmd") 
 
@@ -490,6 +492,10 @@ def cli_main():
        print(" Version:", __version__)
        exit(1)
 
+   if args.usage:
+       print_usage("projit")
+       exit(1)
+
    if args.cmd == None:
        print_usage("projit")
        exit(1)
@@ -536,7 +542,7 @@ def cli_main():
       task_status(project)
 
    if args.cmd == 'render':
-      task_render(project)
+      task_render(project, args.path)
 
 
 ##########################################################################################

### 2023-07-27 docs/paper/paper.tex
Resolving conflicts in paper body

@@
 Scientific practice has expanded to become increasingly dependent of digitial technologies,
-large scale data processing and advanced analytical methods. These shifts have demanded new
-methods of implementing and recording the details of scientific projects. Monolothic applications
-have the advantage of a single and consistent design, however they impede the ability of users to
-innovate and incrementally improve processes. We discuss the qualities of an ideal eScience framework
-for building multi-stage collaboration scientific workflows and present an open source implementation
-for managing data science processes in a decoupled fashion that permits both flexible implementation of
-any stage of processing, and greater ease of meta-data analysis.
+large scale data processing and analytical methods for working with large data volumes. 
+These shifts have demanded new methods of implementing and recording the details of 
+scientific projects. Monolothic applications have the advantage of a single and 
+consistent design, however they impede the ability of users to innovate and 
+incrementally improve processes. We discuss the qualities of an ideal eScience 
+framework for building multi-stage collaboration scientific workflows and present 
+an open source implementation for managing scientific processes in a decoupled 
+fashion that permits both flexible implementation of any stage of processing, 
+and greater ease of meta-data analysis.
 \end{abstract}
@@
 easier to execute and deploy into production systems\cite{Alberti:2018,MolnerDomenech:2020}. 
-To do so they are often constructed for specific combinations of technology. This is a necessary limitation 
-to enable efficiency, but has the effect of limiting general applicability.
+To do so they are often constructed for specific combinations of technology. 
+This is often necessary limitation to either make a project feasible or enable efficiency, 
+but it has the side-effect of limiting general applicability.
 Many other eScience frameworks focus on the lineage and management of data, referred to as 
-the so-called provenance problem \cite{Sahoo:2008,Conquest:2021}
+the so-called provenance problem \cite{Sahoo:2008,Conquest:2021}.
 The goal of the provenance frameworks is sufficient auditibiliy of data that will 
-render eScience transparent and repeatable. This can be auditing of data from multiple source systems,
-auditing of logs generated during data processing\cite{Ferdous2020}. At the extreme we can seek to
-quantify every transformation that happens to data in the course of processing\cite{Sahoo2009}. 
-Regardless of the
-specific data to be audited, these frameworks focus on developing unified systems and processes so
-that auditing can be easily performed over many projects.
+render eScience transparent and repeatable. This can be auditing of data from multiple 
+source systems, or auditing of logs generated during data processing\cite{Ferdous2020}. 
+At the extreme we can seek to quantify every transformation that happens to data in 
+the course of processing\cite{Sahoo2009}. Regardless of the
+specific data to be audited, these frameworks focus on developing unified systems and 
+processes so that auditing can be easily performed over many projects.
 
-In addition to systems for storage of data, eScience application may include facilities for orchestration
-of data processes and external services\cite{Subramanian2013}, requests for experiments with specific 
-parameters\cite{Hunter:2005}, or integrated analysis of results, generation of insights and documentation. 
-Other frameworks and approaches in eScience focus on understanding how to do large scale collaborative science, or
-facilitate meta-level learning of various kinds\cite{Hunter:2005,Liu:2023}. The better we track the
-process of science as a whole, the better we can understand both how to improve scientific processes
-as well as data mine the history of experimental results for phenomena that were difficult to detect.
+In addition to systems for storage of data, eScience application may include facilities
+for orchestration of data processes and external services\cite{Subramanian2013}, 
+requests for experiments with specific parameters\cite{Hunter:2005}, 
+or integrated analysis of results, generation of insights and documentation. 
+Other frameworks and approaches in eScience focus on understanding how to do large 
+scale collaborative science, or facilitate meta-level learning of various 
+kinds\cite{Hunter:2005,Liu:2023}. The better we track the
+process of science as a whole, the better we can understand both how to improve 
+scientific processes as well as data mine the history of experimental results for 
+phenomena that are difficult to detect.
 
-Frameworks for eScience will typically need to take a position on the extent to which they are domain
-specific, versus general purpose. A domain specific approach that integrates multiple data sources in
-a domain aware fashion can faciliate automated or assisted scientific discover\cite{Howe2008}. On the
-other hand a general purpose framework facilitates multi-disciplinary collaboration and permits meta-analysis
-that transcends the boundaries of disciplines. The other key dimension for a decision is the extent to
-which an eScience application depends on specific technologies, many machine learning science platforms
-can provide efficiency gains, but only when using specfic libraries and frameworks\cite{Alberti:2018,MolnerDomenech:2020}.
-Similarly, other empirical science platforms are built on specific database, webserver or application
+Frameworks for eScience will typically need to take a position on the extent to which 
+they are domain specific versus general purpose. A domain specific approach can 
+integrate multiple data sources in a domain aware fashion that can faciliate 
+automated or assisted scientific discover\cite{Howe2008}. On the
+other hand a general purpose framework facilitates multi-disciplinary collaboration 
+and permits meta-analysis that transcends the boundaries of disciplines. 
+The other key dimension for a decision is the extent to which an eScience 
+application depends on specific technologies, many machine learning science platforms
+can provide efficiency gains, but only when using specfic libraries and 
+frameworks\cite{Alberti:2018,MolnerDomenech:2020}. Similarly, other empirical 
+science platforms are built on specific database, webservers or application
 frameworks, which make them less extensible and harder to integrate.
 
-In this work we argue for development of data science frameworks that are minimal in expectations, both in
-terms of appplication domains and underlying technologies. We present a design framework for building
-decoupled data science tools that can improve efficiency and replication through standardisation, without
-unreasonable impositions on design decisions. We describe the design of a open source project integration
-tool (\textit{projit}) that can be used either as a CLI or python API. Internally \textit{projit} depends 
+In this work we argue for development of data science frameworks that impose minimal 
+requirements, both in terms of appplication domains and underlying technologies. 
+We present a design framework for building decoupled data science tools that can 
+improve efficiency and replication through standardisation, without
+unreasonable impositions on design decisions. We describe the design of a open 
+source project integration tool (\textit{projit}) that can be used either as a 
+Command Line Application (CLI) or python API. Internally \textit{projit} depends 
 only on a metadata store that uses the general purpose JSON format. 
 As such it is trivial for developers to build interfaces in other
-languages, or devise web service APIs for decentralised versions. We explore a case study of comparing results
-across multiple projects for which we have used the \textit{projit} application to manage our metadata.
+languages, or devise web service APIs for decentralised versions. We explore a 
+case study of comparing results across multiple projects for which we have used 
+the \textit{projit} application to manage our metadata.
 
@@
 
-We begin by discussing all desirable elements required of an open science framework. These are drawn
-from observations of both how collaborative science works and the successful components of distributed
-scientific endeavours. These requirements are drawn from both sciences that are typically dependent
-on computational frameworks (computer science, bioinformatics, physics) and those that generally are not
+We begin by discussing all desirable elements required of an open science framework. 
+These are drawn from observations of both how collaborative science works and the 
+successful components of distributed scientific endeavours. These requirements are 
+drawn from both sciences that are typically dependent on computational frameworks 
+(computer science, bioinformatics, physics) and those that generally are not
 (social science, psychology).
@@
  \item Sources: Provenance of Data Sources
- \item Processing: Record of Data Processing
- \item Reuse: Facilitating Reuse of Datasets
- \item Tracking: Tracking of Experiments and outputs
+ \item Processing: Records of Data Processing / Transformations
+ \item Reuse: Tooling to Facilitate Reuse of Datasets
+ \item Tracking: Tracking of Experiments and Outputs
  \item Results: Comparison of Methods and Results
- \item Documentation: Generation of Documentation
- \item Reproducibility: Facilitate reproduction of results
- \item Meta-Analysis: Facilitation of Meta-Analysis
+ \item Documentation: Generation of Project Documentation
+ \item Reproducibility: Facilitation of reproduction of results
+ \item Meta-Analysis: Facilitation of Multi-Project Meta-Analysis
 \end{itemize}
 
-The elements in this list are organised in an approximately sequential manner. However, as we discuss
-them below it should be apparent that there are many ways in which these elements support each other.
+The elements in this list are organised in an approximately sequential manner. 
+However, as we discuss them below it should be apparent that there are many ways 
+in which these elements support each other.
 
-First and foremost, data driven projects require a access to the required \textbf{source} data 
-and need to maintain records of this data provenance for \textbf{reproducibility}. 
+First and foremost, data driven projects require access to the required \textbf{source} data 
+and need to maintain records of the data provenance for \textbf{reproducibility}. 
 There will typically be \textbf{processing} applied to these datasets to 
-render them applicable to experimentation and analysis. An ideal tool will track the sequential 
-nature of this \textbf{processing} as well as store information about the location of each resulting dataset.
-The data processed in this way is then available for \textbf{reuse} across experiments and analysis,
+render them applicable to experimentation and analysis. An ideal tool will track the 
+sequential nature of this \textbf{processing} as well as store information about 
+the location of each resulting dataset. The data processed in this way is then 
+available for \textbf{reuse} across experiments and analysis,
 making \textbf{results} comparable.
 
-The centralised storage of data in a unified format allows for scripted generation of \textbf{documentation},
-and facilitates easy \textbf{meta-analysis}. If the product metadata is stored in a public or open source
-repository then it is possible to build tools that extract and process the data from multiple projects. It
-will permit the emgergence of an ecosystem of tools that mine the history of experiments conducted on the
-same or similar source data, evaluate experimental protocols or algorithms across projects and potentially
+The centralised storage of data in a unified format allows for scripted generation 
+of \textbf{documentation}, and facilitates easy \textbf{meta-analysis}. If the 
+product metadata is stored in a public or open source repository then it is 
+possible to build tools that extract and process the data from multiple projects. It
+will permit the emgergence of an ecosystem of tools that mine the history of 
+experiments conducted on the same or similar source data, evaluate experimental 
+protocols or algorithms across projects and potentially
 automate some forms of \textbf{meta-analysis}.
 
-To achieve these advantages we require a uniform system for storing all necessary data that are inputs and outputs 
-for each stage of a data science experiment. The central store permits decoupling of processes by allowing each
+To achieve these advantages we require a uniform system for storing all necessary 
+data that are inputs and outputs for each stage of a data science experiment. 
+The central store permits decoupling of processes by allowing each
 element of the process to be implemented and executed independently of the others.
@@
 and analysis of results all happen independently. Each of them accesses the projit metadata 
-store for the information they need, and subsequently store information and results once complete.
-This process means that in principle the location of an underlying dataset could change without
-modifying other elements of the project. Similarly, we might change the parameters or an experiment
-or the set of metrics we calculate. Each experiment and analysis task operates independently of the
-others, and all that suffers when changes are made is the potential for comparison across equal
-dimensions of variation.
+store for the information they need, and subsequently store information and results once 
+complete. This process means that in principle the location of an underlying dataset 
+could change without modifying other elements of the project. Similarly, we might change 
+the parameters or an experiment or the set of metrics we calculate. Each experiment and 
+analysis task operates independently of the others, relying on the meta-data store for 
+dependencies rather than direct communication. When changes are made there might be a
+loss of synchronisation between elements, for example between test data and results. 
+This issue can only be addressed by extending the project with a dependency graph for 
+capturing, and potentially orchestrating, processing pipelines.
 
-In addition to the dominant requirements of experimentation (parameter and results) we store the results
-of each experimental execution as well as the experiment duration, measured from the time of initiation
-to completion. These records are particularly important in data science and machine learning where we
-may want to trade off performance with computational requirements. But these values could be used to store
-information about real world experimtal execution, or the time required to marshal and sequence a series
-of independent web services.
+In addition to the dominant requirements of experimentation (parameters and results) we 
+store the results of each experimental execution as well as the experiment duration, 
+measured from the time of initiation to completion. These records are particularly 
+important in data science and machine learning where we may want to trade off 
+performance with computational requirements. But these values could be used to store
+information about real world experimental execution or the time required to marshall 
+and sequence a series of independent web services.
+
+The project utilises a notion of key asset types: dataset, experiment and results. Each
+of these can be created independently with a reference between them in a loose coupling.
+In addition, a tagging system allows these assets to be labelled with an open ended number
+of tags that cen be used when extracting or tabulating project properties.
 
@@
 
-Projit has been implemented as python package that functions as both a command line application
-and library that can be included inside other scripts and applications. The command line application
-can be used to query the project metadata in much the same way that the git application can be used.
-A user can add, modify and list the collection of analytical assets in the project: datasets, experiments 
-parameters, tags and results are all accessible from the command line application.
+Projit has been implemented as python package that functions as both a command line 
+application and library that can be included inside other scripts and applications. 
+The command line application can be used to query the project metadata in much the 
+same way that the git application can be used to manipulate a query a set of software
+source files. A user can add, modify and list the collection of assets in the 
+project: datasets, experiments and results are all accessible from the command line 
+application.
 
-The python package can be included in a script so that the script can access the project metadata store.
-This allows the script to find the location of common datasets, register themselves as an experiment
-and store results once the script is complete. Programmatic interaction with the project data through
-the projit API is what permits the scripts of a project to be decoupled and contribute to the project
-without being aware of how any other element is structured or implemented. Furthermore, as the metadata
-is stored locally in standard JSON files, these can be stored inside a cloud repository and then contributed
-to by collaborators. This allows distributed data science teams to define their own lines of experimentation,
-but use a synchronised data set then continually contribute to a central meta-data store of project results.
+The python package can be included in a script so that the script can access the 
+project metadata store. This allows the script to find the location of common 
+datasets, register themselves as an experiment or execution and store results once 
+the script is complete. Programmatic interaction with the project data through
+the projit API is what permits the scripts of a project to be decoupled and 
+contribute to the project without being aware of how any other element is 
+structured or implemented. Furthermore, as the metadata
+is stored locally in standard JSON files, these can be stored inside a cloud 
+repository and then contributed to by collaborators. 
+This allows distributed data science teams to define their own lines of experimentation,
+but use a synchronised data set then continually contribute to a central meta-data 
+store of project results.
 
@@
 
-We have utilised the projit application across multiple data science projects to store reusable datasets
-and the results of all experiments. Additionally, the metadata store contains infomation about the number
-of times each experiment has been executed, and the execution time utilised on each run. This allows us
-to generate an ad hoc script that can compare projects in terms of the data used, the number of experiments
-conducted and the total execution time. This script is constructed for illustrative purposes to show that
-the projit tool can permit arbitrary meta-analysis of projects through the standardised metadata stored across
-git repositories.
+We have utilised the projit application across multiple data science projects to store 
+reusable datasets and the results of all experiments. Additionally, the metadata store 
+contains information about the number of times each experiment has been executed, 
+and the execution time utilised on each run. This allows us to generate an ad hoc 
+script that can compare projects in terms of the data used, the number of experiments
+conducted and the total execution time. This script is constructed for illustrative 
+purposes to show that the projit tool can permit arbitrary meta-analysis of projects 
+through the standardised metadata stored across git repositories.
 

### 2023-10-12 docs/paper/paper.tex
Paper update

@@
 
-%%
-%% \BibTeX command to typeset BibTeX logo in the docs
-\AtBeginDocument{%
-  \providecommand\BibTeX{{%
-    Bib\TeX}}}
+\usepackage{listings}
+\usepackage{graphicx}
+\usepackage{graphics}
+\usepackage{geometry}
+\usepackage{xcolor}
+\usepackage{anyfontsize}
+
+\definecolor{codegreen}{rgb}{0,0.6,0}
+\definecolor{codegray}{rgb}{0.5,0.5,0.5}
+\definecolor{codepurple}{rgb}{0.58,0,0.82}
+\definecolor{backcolour}{rgb}{0.95,0.95,0.92}
+\lstdefinestyle{mystyle}{
+    backgroundcolor=\color{backcolour},
+    commentstyle=\color{codegreen},
+    keywordstyle=\color{magenta},
+    numberstyle=\color{codegray},
+    stringstyle=\color{codepurple},
+    basicstyle=\ttfamily\footnotesize,
+    breakatwhitespace=false,
+    breaklines=true,
+    captionpos=b,
+    keepspaces=true,
+    numbers=left,
+    numbersep=5pt,
+    showspaces=false,
+    showstringspaces=false,
+    showtabs=false,
+    tabsize=2
+}
+\lstset{style=mystyle}
 
@@
 knowledge of each others work, and producing a factory line of un-reproducible results 
-\cite{Ioannidis2005}.
+\cite{Ioannidis2005}. This cost is compounded by the problems of increasingly 'Big Data' 
+based science, where the logistics of maintaining and tracking data sets is challenging.
+While big data may offer many opportunities cross-disciplinary and algorithmic science\cite{Schmitt2015}, 
+there is a strong concern that this will be limited\cite{Succi2019}, 
+and that the core scientific tasks of conceiving,
+designing and running experiments needs to be managed at an ever increasing scale.
 
-Many Machine Learning experimentation frameworks focus on the task of making experiments
-easier to execute and deploy into production systems\cite{Alberti:2018,MolnerDomenech:2020}. 
-To do so they are often constructed for specific combinations of technology. 
-This is often necessary limitation to either make a project feasible or enable efficiency, 
-but it has the side-effect of limiting general applicability.
-Many other eScience frameworks focus on the lineage and management of data, referred to as 
-the so-called provenance problem \cite{Sahoo:2008,Conquest:2021}.
-The goal of the provenance frameworks is sufficient auditibiliy of data that will 
+Platforms for eScience offer a variety of solutions for these problems including  
+tracking the lineage and management of data, referred to as 
+the provenance problem \cite{Sahoo:2008,Conquest:2021}.
+The goal of provenance frameworks is sufficient auditibiliy of data that will 
 render eScience transparent and repeatable. This can be auditing of data from multiple 
@@
 specific data to be audited, these frameworks focus on developing unified systems and 
-processes so that auditing can be easily performed over many projects.
+processes so that auditing can be easily performed over many projects. It has been 
+argued that tracking meta-data is critical for the endeavour of large scale open and auditable 
+science\cite{Reznik2022}. It is only through meta-data that we are able to build frameworks
+that can understand and assist the scientific process.
 
-In addition to systems for storage of data, eScience application may include facilities
+In addition to systems for tracking data, eScience application may include facilities
 for orchestration of data processes and external services\cite{Subramanian2013}, 
@@
 
-In this work we argue for development of data science frameworks that impose minimal 
-requirements, both in terms of appplication domains and underlying technologies. 
-We present a design framework for building decoupled data science tools that can 
-improve efficiency and replication through standardisation, without
-unreasonable impositions on design decisions. We describe the design of a open 
-source project integration tool (\textit{projit}) that can be used either as a 
-Command Line Application (CLI) or python API. Internally \textit{projit} depends 
-only on a metadata store that uses the general purpose JSON format. 
-As such it is trivial for developers to build interfaces in other
-languages, or devise web service APIs for decentralised versions. We explore a 
-case study of comparing results across multiple projects for which we have used 
-the \textit{projit} application to manage our metadata.
-
-\section{Methodology}
+Many Machine Learning experimentation frameworks focus on the task of making experiments
+easier to execute and deploy into production systems\cite{Alberti:2018,MolnerDomenech:2020}.
+To do so they are often constructed for specific combinations of technology.
+This is often necessary limitation to either make a project feasible or enable efficiency,
+but it has the side-effect of limiting general applicability. An ideal data science
+framework would allow open ended experimentation, with an ability for easy tracking
+and comparison of these experiments.
 
@@
 
-We begin by discussing all desirable elements required of an open science framework. 
+In this work we argue for the development of data science frameworks that impose minimal 
+requirements, both in terms of appplication domains and underlying technologies. 
+We present a design framework for building decoupled data science tools that can 
+improve efficiency and replication through standardisation, without
+unreasonable impositions on design decisions. We describe the design of a open 
+source meta-data tracking project integration tool (\textit{projit}) that can be used either as a 
+Command Line Application (CLI) or python API. Internally \textit{projit} depends 
+only on a simple metadata store that uses the general purpose JSON format. 
+As such it is trivial for developers to build interfaces in other
+languages, or devise web service APIs for decentralised versions. We explore a 
+case study for analysing a project for which we have used 
+the \textit{projit} application to manage our experiment metadata.
+
+\section{Methodology}
+
+We begin by discussing the desirable features of an open science framework. 
 These are drawn from observations of both how collaborative science works and the 
@@
 
+\begin{lstlisting}[language=BASH,label={code:install}, caption=Installation and Invocation of Projit CLI]
+pip install projit
+
+projit init "Test Project"
+\end{lstlisting}
+
 The python package can be included in a script so that the script can access the 
@@
 
+\begin{lstlisting}[language=Python,label={code:usage}, caption=Usage of Projit Python Library]
+import projit as pit
+
+experiment_name = "My Experiment"
+project = pit.projit_load()
+exec_id = project.start_experiment(experiment_name, sys.argv[0], params={})
+#
+# EXPERIMENT EXECUTION CODE 
+#
+project.end_experiment(experiment_name, exec_id)
+\end{lstlisting}
+
 \section{Case Study}
@@
 We have utilised the projit application across multiple data science projects to store 
-reusable datasets and the results of all experiments. Additionally, the metadata store 
+references to reusable datasets and experimental resultss. Additionally, the metadata store 
 contains information about the number of times each experiment has been executed, 
-and the execution time utilised on each run. This allows us to generate an ad hoc 
-script that can compare projects in terms of the data used, the number of experiments
-conducted and the total execution time. This script is constructed for illustrative 
-purposes to show that the projit tool can permit arbitrary meta-analysis of projects 
-through the standardised metadata stored across git repositories.
+and the execution time utilised on each run. This allows us to conduct an after-the-fact
+investigation into these projects. In this section we demonstrate how some details of these
+projects can be revealed through the project meta-data.
+
+\subsection{Systematic Review with Machine Learning}
+
+In a recent paper we explored the use of machine learning algorithms for filtering a initial
+set of article abstracts as part of a systematic review\cite{HawkinsTivey2023}. 
+The resulting paper focused on four
+different machine learning strategies, the first of which were standard machine learning techniques
+trained on simple features, such as the age of the article, the number of authors, the number of 
+matching keywords in the abstract etc. The presentation of results in this paper created the impression
+that all of these baseline models were executed in the first round of experimentation. By querying
+the \emph{projit} meta-data store to fine the first execution time of each experiment, we created
+Table \ref{tab:execs}, which shows that he Naive Bayes and SVM models were in fact executed last.
+
+\begin{table}
+\caption{Experiment Executions}
+\label{tab:execs}
+\resizebox{\columnwidth}{!}{%
+\begin{tabular}{|l|r|r|}
+\toprule
+Experiment            &Execution Count    &First Execution     \\
+\midrule
+Dataset Size         &1                   &2   \\
+Variables            &11                  &1      \\
+Outlier Proportion   &2                   &0  \\
+Std Multiplier       &6                   &     \\
+\bottomrule
+\end{tabular}
+}
+\end{table}
+
+In our case this was because extended literature reviews indicated that many people working on this
+problem previously tended to rely on one of these two techniques. It was decided that we should include
+them in our baselines, as a reasonable reviewer response would be to ask why we did not include these
+models for comparison (given their prevalance in the literature). An ability to query meta-data about
+experimentation, can reveal clues as to the way a piece of research was conducted, and raise valuable
+questions that might be needed to detect suspicious activity.
 
 \section{Conclusion}
+
+Modern science has faced multiple problems with repeatability, credibility and feasibility. The problems
+we want to solve require more and more large scale digital assets and technologies, and we require methods 
+for tracking and managing this growing complexity. These problems exist in academic science and in industry
+practices like data science, where organisations are investing to create reusable technologies and 
+competitive advantages.
+
+We have argued for a decoupled approach to building eScience tools. One that draws inspiration from the Unix
+philosophy of make simple interoperable tools. This approach will allow us to create an open and easily 
+adaptable set of tools that can support many kinds of scientific projects.
+
+We have implemented a simple meta-data management tool using these ideas and released it as an open source 
+library and python package. The \emph{projit} tool can be used to track datasets, experiments and results
+for any project that uses algorithms or scripting.
+
+Finally, we provided a simple example of using this meta-data to query the experimental details behind one
+of our previous research projects. Highlighting how \emph{projit} can be used to audit a project and identify
+the experimental realities behind a set of results.
 

### 2024-09-27 setup.py
Adding setuptools to requirements Mergining with other changes to requirements

@@ -18,7 +18,7 @@ setup(
     name = "projit",
     packages = ["projit"],
     license = "MIT",
-    install_requires = ['numpy', 'pyyaml', 'pandas', 'fpdf', 'gitpython'],
+    install_requires = ['numpy', 'pyyaml', 'pandas', 'fpdf', 'gitpython', 'setuptools'],
     entry_points = {
         "console_scripts": ['projit = projit.cli:main']
     },

### 2024-09-29 docs/paper/paper.tex
Working on JOSS submission
Working on JOSS paper draft

@@
 
+Software approaches to managing data, processes and meta-data are typically referred to 
+as e-science platforms. In general they are either build for specific scientific domains
+\cite{Howe2008,} or they are designed for very specific technology stacks (common in a given domain)
+\cite{Subramanian2013}.
+
 Platforms for eScience offer a variety of solutions for these problems including  
@@
 integrate multiple data sources in a domain aware fashion that can faciliate 
-automated or assisted scientific discover\cite{Howe2008}. On the
+automated or assisted scientific discovery\cite{Howe2008,Pettit:2010}. On the
 other hand a general purpose framework facilitates multi-disciplinary collaboration 
@@
 \begin{figure*}
-\includegraphics[scale=0.6]{./Projit_decoupled_process.drawio.png}
+\includegraphics[scale=0.6]{./images/Projit_decoupled_process.drawio.png}
 \caption{Projit Process for Decoupled Data Science}

### 2024-11-08 docs/paper/escience/paper.tex
Clean up docs/paper folder for JOSS submission

--- 2024-09-29 docs/paper/paper.tex
@@
 
-Software approaches to managing data, processes and meta-data are typically referred to 
-as e-science platforms. In general they are either build for specific scientific domains
-\cite{Howe2008,} or they are designed for very specific technology stacks (common in a given domain)
-\cite{Subramanian2013}.
+Software approaches to managing scientific data, processes and meta-data are typically referred to 
+as e-science platforms. In general they are either built as front-ends for specific 
+scientific domains \cite{Howe2008,Pettit:2010} (leveraging known analytical practices in
+the given domain) or they are designed to faciliate interoperability between different
+technology stacks \cite{Subramanian2013}. Machine learning focused frameworks tend to 
+focus on solving problems of model training and deployment for specific technologies\cite{Alberti:2018,MolnerDomenech:2020}, and hence have limited generality.
 
